### 2016-02-19 paper.tex
Note how lower solidity turbines will operate at higher TSR

The present study was motivated by the need to acquire a new experimental
dataset for the lower solidity RM2 turbine at sufficient Reynolds numbers to be
relevant to full-scale modeling. It was hypothesized that the parasitic losses
from rotor blade support struts could play an important role in overall turbine
performance. Thus, the parasitic torque from strut drag was measured without
blades, then deliberately and significantly increased in the physical model to
provide data to investigate its importance. The velocity field in the near-wake
of the turbine was then measured to compare with measurements from a higher
solidity rotor in the same experimental setup \cite{Bachant2015-JoT}, and
provide validation data for numerical models that predict wake flows, which
determine turbine--turbine interaction and optimal spacing for turbine arrays.
This dataset, along with the code for processing and visualization, is publicly
available (licensed via Creative Commons CC-BY for data and MIT license for
code) as a Git repository on GitHub
(\url{https://github.com/UNH-CORE/RM2-tow-tank}) and as a citeable archive with
a digital object identifier (DOI) \cite{Bachant2015-RM2-data}.

>>>>

The present study was motivated by the need to acquire a new experimental
dataset for the lower solidity RM2 turbine at sufficient Reynolds numbers to be
relevant to full-scale modeling. It was hypothesized that the parasitic losses
from rotor blade support struts could play an important role in overall turbine
performance, especially for a lower solidity turbine that operates at higher tip
speed ratios. Thus, the parasitic torque from strut drag was measured without
blades, then deliberately and significantly increased in the physical model to
provide data to investigate its importance. The velocity field in the near-wake
of the turbine was then measured to compare with measurements from a higher
solidity rotor in the same experimental setup \cite{Bachant2015-JoT}, and
provide validation data for numerical models that predict wake flows, which
determine turbine--turbine interaction and optimal spacing for turbine arrays.
This dataset, along with the code for processing and visualization, is publicly
available (licensed via Creative Commons CC-BY for data and MIT license for
code) as a Git repository on GitHub
(\url{https://github.com/UNH-CORE/RM2-tow-tank}) and as a citeable archive with
a digital object identifier (DOI) \cite{Bachant2015-RM2-data}.
